---
title: "Mariiage license Data"
author: 
  - Akshat Aneja
thanks: "Code and data are available at: https://github.com/Akshat211202/Reflection-Excercise-3"
date: 19 Septmeber 2024
date-format: long
abstract: Data for marriage licenses
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```

# Introduction

You can and should cross-reference sections and sub-sections. We use @talia, @opendatatorotno, and @rohan.

The remainder of this paper is structured as follows. @sec-mydatasection

# Data {#sec-mydatasection}

Some of our data is of penguins (@fig-marriage), from @palmerpenguins.

```{r}
#| label: fig-marriage
#| fig-cap: Marriage Licenses issued
#| echo: false

data |>
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point() +
  labs(title = "Marriage Licenses Issued",
       x = "Year",
       y = "Licenses")
```

The graph shows a stable pattern of marriage licenses issued from 2010 to 2019, with some cyclic trends, likely seasonal. Around 2020, there's a sharp decline, likely due to the COVID-19 pandemic. From 2021 onwards, there's a significant surge in licenses, possibly due to postponed weddings and societal recovery post-pandemic.


\newpage

# References
